The Effects of the NBA COVID Bubble on the NBA Playoffs: A Case Study for Home-Court Advantage

### 2022-02-05 Manuscript/Response_To_Comments.tex

\begin{center}
  {\Large\bf Response to the Comments on Manuscript}
\end{center}

\section*{Summary}
\jy{Practice the line width style in tex source}

We thank the two referees for their insightful, constructive
comments. In particular, we are grateful to referee~1 for providing
many helpful, direct and concise comments using annotations. Also, to
referee~2, who took the time to provide detailed explanations for each
suggestion making it clear how and why the changes were important.

The manuscript has been revised to incorporate the comments from the
referees with the following most notable additions:

@@

\begin{enumerate}
\item
  Additional commentary and thoughts on what caused away teams to be more affected by neutral courts more than home teams.
  \item
  A deeper discussion on the significance and impact of the shift in two-point shooting.
\item
  Alterations to graphs and charts to better and more clearly describe the data and findings.
\end{enumerate}

Point-by-point responses are as follows with the original comments in \emph{italic}.

\jy{In each response, be more specific on the location of the changes made (give
  paragraph numbers in which section)}

@@

% \begin{comment}
% Comments in the pdf. 
% \end{comment}

There were a series of brief comments provided on an annotated version of our manuscript submission. This included many small comments for missing words or asking for a brief clarification about a point made. These comments were addressed accordingly and were resolved. The more extensive comments/concerns are addressed individually below.

\begin{comment}
  Reference lines (mean/median) would be nice in the graphs to more clearly see the small shifts.
\end{comment}

The figures were remade with added reference line at the mean for all applicable histograms.

@@

 We thank the reviewer for being appreciative and understanding of the good motivations driving this paper. We agree that a deeper discussion of why home-court advantage would not exist in the bubble would be beneficial to setting up the paper. We added in a discussion of why all the different factors play into creating home-court advantage and how each one may or may not still exist in the bubble. For the most part, these factors disappeared in the context of the bubble, except travel/time and miles for reasons we discuss in the paper.

\begin{comment}
Also, this paper https://arxiv.org/abs/1701.05976 finds that altitude matters (Colorado and Utah teams
have the highest home advantage in multiple sports), so that could be added/discussed. So changes in home
advantage in the bubble could impact teams differently, and NBA teams Nuggets and Jazz could be hurt
more than other teams since they no longer benefit from an altitude advantage.
\end{comment}

 We are very grateful that referee~2 brought \citet{Lopez} to our attention. It was added to Literature Review and discussed in the Introduction when setting up and explaining the factors that would be missing from normal home-court advantage when playing in the NBA bubble. The most noteworthy point added from this paper, as pointed out by referee~2, was the evidence supporting geographic factors impact home-court advantage. Particularly, teams like the Utah Jazz and Denver Nuggets are the NBA teams who would benefit from the high-altitude effects. This is discussed in more detail in the manuscript.

 \jy{Check the references of Lopez's paper to see if we can cite
   anything there; this is also a place to mention the additional
   references you found. }

### 2022-02-05 Manuscript/manuscript.tex
comments on revised manuscript and response

% These commands change the font. If you do not have Garamond on your computer, you will need to install it.
\usepackage{garamondx}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amsthm}
\usepackage{graphicx}
\usepackage{hyperref}

@@

% Add author information below. Communicating author is indicated by an asterisk, the affiliation is shown by superscripted lower case letter if several affiliations need to be noted.
\author{
Michael Price*$^{a}$, Jun Yan \\ \medskip 
$^{a}$Department of Statistics, University of Connecticut, Storrs, CT  \\  \medskip 
% \\ \medskip 
Students: michael.price@uconn.edu* \\
Mentor: jun.yan@uconn.edu 
}

@@

Home-court advantage is often discussed in sports circles as a contributing
factor to the outcome of games. It is well-known that the home team typically
benefits from some competitive edge while playing at their homecourt, resulting
in a better chance of winning. Thus, the NBA playing the 2020 playoffs in a
bubble due to the COVID-19 pandemic
brought a great deal of concern for fans, teams, journalists, and others. The bubble
environment would not be able to replicate many of the factors that normal home-court
advantage relies on. Among the biggest is the effect from the crowd. The home crowd has
the ability to energize home teams, help control momentum in favor of the home team and 
create a chaotic and stressful environment for away teams to play in. There is no way
to replicate these effects in the bubble conditions. Also, there are geographic factors
that are lost, like altitude and time-zone effects. There's evidence across all sports
that teams in high altitude regions can rely on away teams coming in and struggling with
the lower oxygen levels at a higher altitude, which the home teams are accustomed to playing
with \citet{Lopez}. Examples of high altitude teams in the NBA would be the Utah Jazz
and Denver Nuggets, both of whom participated in the 2020 NBA bubble. Also, referees 
are known to be subject to favoring home teams. This is due in large part to pressure
from fans, which is no longer in play in the bubble. Refs may still have biases, but 
there's nothing to sway that bias towards the home team like normal. Any positive
effects of the home team playing in the arena they're most comfortable in and
living in the comfort of their own home are also lost. Travel is also normally 
discussed as a factor hurting away teams, but in the context of the playoffs
being played in the bubble, losing this may not be significant. In the playoffs,
many times (aside from the first game of the series when the away team travels), 
both teams often travel at the same time, since they're both going back and forth
between the two cities to complete the series.

@@

We will compare home team performance in 2020 at a neutral site with
no fans vs.~2017-19 playoffs with fans. Likewise, away team performance in 2020
at a neutral site with no fans vs.~2017-19 playoffs with fans. By comparing home
teams in 2020 to home teams in 2017-19 and away teams in 2020 to away teams in
2017-19, we add a new perspective to the field of research. This will allow for
a more accurate understanding of the effects of home-court advantage on home and
away teams in the NBA. We will not only see that home-court advantage helps home
teams outperform away teams, but also separate the
effects of home-court advantage on home teams' and away teams' performance individually.

Nine hypotheses were tested to understand the differences in 2020 vs.~earlier
years. First, whether or not the difference between home win percentage in 2020
and 2017-19 is zero. This difference is found to be statistically
significant from zero. Then we assess for differences in home
scoring in 2020 vs 2017-2019. Similarly, we can do the same test, but for
differences in away scoring in 2020 vs 2017-2019. Also, differences in team
shooting (for two-pointers, three-pointers, and free throws) from 2020 vs 2017-2019
for both home and away teams. The results from these tests bring a new perspective
to the understanding of how home-court advantage impacts games by altering the performance
of the home and away teams.

\section{Literature Review}
There is voluminous literature on the effects of home-court advantage.
Many NBA home-court advantage studies analyze the effects by studying shooting
percentages. \citet{Kotecki} reported significant evidence of home-court
advantage by comparing field goal
percentage, free throw percentage and points scored in home vs.~away teams.
He found all of these measures showed evidence that
home-court advantage helps home teams play better. \citet{Cao} studied the effects
of pressure on performance in the NBA. Using free throws as their measure of interest, 
they tested whether home
fans could distract and put pressure on opposing players to make free
throws. However, they did not find significant evidence
that home status has a substantial impact on missing from the free throw line. 
\citet{Harris} used two-point shots, three-point shots and free
throws as measures of interest to study home-court advantage. Two-point
shots were found to be the strongest predictor of home-court advantage. They
suggested that home teams should try to shoot more two-point shots and force
their opponent to take more two-point shot attempts. This help home teams have a
greater control of the game play and help maximize the benefits 
home-court advantage.

@@

Home-court advantage is the basic idea that the home team is more likely to win given 
they benefit from positive effects of a few factors we discussed earlier.
So laying a foundation of typical home-court advantage is crucial. Before
focusing on the 2017 to 2020 playoffs, we can take a quick look at home team win
percentages since 2010. Notice in Figure \ref{fig:Fig1}, the 10 years before 2020, the home team
winning percentage ranged from around 0.56 to 0.7 and never dipped below 0.5. The
2020 bubble broke this historic pattern, dipping down below 0.5. Foreshadowing
the confirmation of the expectation that the effect of home-court advantage was removed
in the 2020 playoffs.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.4\linewidth]{Fig1}
  \caption{Winning percentage of NBA home teams in the playoffs since
    2010, the green line denotes .500.}
  \label{fig:Fig1}
\end{figure}

Moving on to the main focus of the study, comparing 2020 to 2017-2019.
Figure \ref{fig:Fig2} shows the histograms of the home (green) and
away scoring (red) for 2020 vs.~2017-2019. All histograms are
fairly bell shaped, which is important for statistical tests
designed for normally distributed data. There appears to be little
difference between the 2020 and 2017-2019 for home scoring. For
away scoring, a more pronounced shift to the right in 2020 is observed
compared to 2017-2019.

@@

Our second target of inference is shooting percentage for home and away teams.
Figure \ref{fig:Fig3} shows home shooting for two-pointers, three-pointers and
free throws for 2020 (top) vs.~2017-19 (bottom). The histograms appear to be fairly
similarly distributed between 2020 and 2017-19. Likewise, Figure \ref{fig:Fig4},
shows the same percentages except for away teams. It appears that the
two-point shooting percentage for away teams has a small shift to the
right in 2020 relative to 2017-2019.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.4\linewidth]{Fig3}
  \caption{Histograms of home shooting percentages for two-
    pointers, three-pointers and free throws for 2020 (top) vs.~2017-19
    (bottom).}
  \label{fig:Fig3}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.4\linewidth]{Fig4}
  \caption{Histograms of away shooting percentages for two-pointers,
    three-pointers and free throws for 2020 (top) vs.~2017-19
    (bottom).}
  \label{fig:Fig4}  
\end{figure}

@@

Comparisons between 2020 and 2017-19 home and away teams were made on home team
winning percentage, total team scoring and two-point, three-point and free throw
shooting. Comparing the differences in these metrics for home and away teams in
2020 vs previous years will provide valuable insights to the understanding of
home-court advantage. We can see how going on the road may negatively impact
away performance and how playing at home may positively impact home performance.
If there are differences in scoring for home or away teams, the differences can
be used to show how home-court advantage affects the overall performance of home
and away teams. While testing for differences in shooting will provide added
context for how home-court advantage specifically affects performance.
Shooting percentages are not the only possible metrics affected by home-court
advantage, but they are the most obvious and likely most important one.

@@

\section{Results}
\bigskip
\begin{table}[H]
  \caption{The results from the 9 tests(* denotes significant p-value at alpha=0.05)
  \\*Note: Home and Away scoring totals are divided by 100}
  \label{tab:table}
\centering
\begin{tabular}[t]{lcccccc}
  & 2020 & 2017-19 & \multicolumn{2}{c}{P-value} & \multicolumn{2}{c}{Adjusted P-value}\\
  &          &                & Z-test & Wilcoxan & Z-test & Wilcoxan\\
Home Win & 0.482 & 0.613 & 0.0497* & 0.0400* & .4473 & 0.3598\\
Home Scoring & 1.101 & 1.081 & 0.2321 & 0.2985 & 1 & 1\\
Away Scoring & 1.091 & 1.040 & 0.0008* & 0.0004* & 0.0075* & 0.0035*\\
Home 2P & 0.523 & 0.515 & 0.4335 & 0.5719 & 1 & 1\\
Home 3P & 0.363 & 0.357 & 0.5733 & 0.8852 & 1 & 1\\
Home FT & 0.793 & 0.774 & 0.0692 & 0.0496* & 0.6228 & 0.4464\\
Away 2P & 0.536 & 0.504 & 0.0003* & 0.0003* & 0.0030 & 0.0023\\
Away 3P & 0.357 & 0.346 & 0.3256 & 0.3081 & 1 & 1\\
Away FT & 0.783 & 0.777 & 0.6601 & 0.8370 & 1 & 1\\
\end{tabular}
\end{table}

Starting from the top of the
Table \ref{tab:table} summarizes p-values of the nine hypotheses for both
\(z\)-tests and Wilcoxon tests. The p-values are all fairly similar for both
tests giving strong confidence in the conclusions drawn. Also, reported are
the point estimates of the two samples in each comparison.

First, we see a statistically significant change
in home win percentage in 2020 from 2017-19, with a p-value of 0.0497 for the
\(z\)-test and 0.0400 for Fisher's exact test. The 95\% confidence
interval (CI) of \((-0.255, -0.008)\)
confirms our belief that home-court advantage was lost in the 2020 NBA 
playoffs. However, after accounting for
multiple tests using the Bonferroni correction, the p-values for both
tests are no longer significant. So, we may only cautiously say there is 
evidence that home-court advantage was
not a factor in 2020.

Home team performance did not seem to be negatively impacted by losing home-court
advantage like expected. Home scoring, two-point and three-point shooting
shooting all show no significant difference, on average, between 2020 vs.
2017-19 based on p-values from both tests. However, the Wilcoxon test and \(z\)-test have conflicting results
for free throws. The \(z\)-test p-value of 0.0692 indicates no significant difference, while
the Wilcoxon test p-value of 0.0469 indicates a difference at the 5\% significance level. Since
the p-value of the Wilcoxon test is so close to significance level and neither p-value is significant
after a Bonferonni correction for multiple tests, this difference is likely not very meaningful.
There appears to be no strong evidence suggesting home teams played at
a lower level in 2020 than they did in previous years when they had home-court advantage.

@@

\section*{acknowledgements}
The authors thank the University of Connecticut and the UConn Department of Statistics.
%Note correct LaTeX quotations above. Do not use the " symbol, but rather double ` followed by double '

@@

% The Press Summary section is NOT optional.  Write a paragraph describing the paper in a manner suitable for the press; see previous journal editions for examples.
\section*{press summary}
The purpose of this study was to examine the 2020 NBA playoffs, which were played inside of a bubble in Disney World because of the COVID-19 pandemic. The hope was to generate new insights about the effects of home-court advantage because the bubble created an unprecedented neutral playing field for the NBA. For the first time the effects of home-court advantage on home and away teams could be easily separated and studied individually, typically studies can only compare them relative to each other. This study is focused on team scoring totals and team shooting percentage on two-pointers, three-pointers, and free throws. Comparing these measures for home teams and away teams in 2020 vs. 2017-2019 shows that the 2020 playoffs favored away teams more than usual, particularly with two-point shooting and total scoring. The implication of these findings is home-court advantage seems to be the result of negative effects on away team, not positive effects on home-team.

>>>>

% These commands change the font. If you do not have Garamond on your computer, you will need to install it.
\usepackage{garamondx}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\newcommand{\jy}[1]{\textcolor{orange}{JY: (#1)}}
\usepackage{booktabs}

@@

% Add author information below. Communicating author is indicated by an asterisk, the affiliation is shown by superscripted lower case letter if several affiliations need to be noted.
\author{
Michael Price*, Jun Yan \\ \medskip 
Department of Statistics, University of Connecticut, Storrs, CT  \\  \medskip 
Students: michael.price@uconn.edu* \\
Mentor: jun.yan@uconn.edu 
}

@@

Home-court advantage is often discussed in sports circles as a contributing
factor to the outcome of games. It is well-known that the home team typically
benefits from some competitive edge while playing at their home court, resulting
in a better chance of winning. Thus, the NBA playing the 2020 playoffs in a
bubble due to the COVID-19 pandemic
brought a great deal of concern for fans, teams, journalists, and others. The bubble
environment would not be able to replicate many of the factors that normal home-court
advantage relies on. Among the biggest is the effect from the crowd. The home crowd has
the ability to energize home teams, help control momentum in favor of the home team and 
create a chaotic and stressful environment for away teams to play in. There is no way
to replicate these effects in the bubble conditions. Also, there are geographic factors
that are lost, like altitude and time-zone effects. There's evidence across all sports
that teams in high altitude regions can rely on away teams coming in and struggling with
the lower oxygen levels at a higher altitude, which the home teams are accustomed to playing
with \citet{Lopez}. Examples of high altitude teams in the NBA would be the Utah Jazz
and Denver Nuggets, both of whom participated in the 2020 NBA bubble. Also, referees 
are known to be subject to favoring home teams. This is due in large part to pressure
from fans, which is no longer in play in the bubble. Refs may still have biases, but 
there's nothing to sway that bias towards the home team like normal. Any positive
effects of the home team playing in the arena they're most comfortable in and
living in the comfort of their own home are also lost. Travel is also normally 
discussed as a factor hurting away teams, but in the context of the playoffs
being played in the bubble, losing this may not be significant. In the playoffs,
many times (aside from the first game of the series when the away team travels), 
both teams often travel at the same time, since they're both going back and forth
between the two cities to complete the series.

@@

We will compare home team performance in 2020 at a neutral site with
no fans vs.~2017--19 playoffs with fans. Likewise, away team performance in 2020
at a neutral site with no fans vs.~2017--19 playoffs with fans. By comparing home
teams in 2020 to home teams in 2017--19 and away teams in 2020 to away teams in
2017--19, we add a new perspective to the field of research. This will allow for
a more accurate understanding of the effects of home-court advantage on home and
away teams in the NBA. We will not only see that home-court advantage helps home
teams outperform away teams, but also separate the
effects of home-court advantage on home teams' and away teams' performance individually.

Nine hypotheses were tested to understand the differences in 2020 vs.~earlier
years. First, whether or not the difference between home win percentage in 2020
and 2017--19 is zero. This difference is found to be statistically
significant from zero. Then we assess for differences in home
scoring in 2020 vs 2017-2019. Similarly, we can do the same test, but for
differences in away scoring in 2020 vs 2017-2019. Also, differences in team
shooting (for two-pointers, three-pointers, and free throws) from 2020 vs 2017-2019
for both home and away teams. The results from these tests bring a new perspective
to the understanding of how home-court advantage impacts games by altering the performance
of the home and away teams.

\section{Literature Review}

\jy{add some references from google scholar search ``home team
  advantage nba''; we have only 10 references now.}

There is voluminous literature on the effects of home-court advantage.
Many NBA home-court advantage studies analyze the effects by studying shooting
percentages. \citet{Kotecki} reported significant evidence of home-court
advantage by comparing field goal
percentage, free throw percentage and points scored in home vs.~away teams.
He found all of these measures showed evidence that
home-court advantage helps home teams play better. \citet{Cao} studied the effects
of pressure on performance in the NBA. Using free throws as their measure of interest, 
they tested whether home
fans could distract and put pressure on opposing players to make free
throws. However, they did not find significant evidence
that home status has a substantial impact on missing from the free throw line. 
\citet{Harris} used two-point shots, three-point shots and free
throws as measures of interest to study home-court advantage. Two-point
shots were found to be the strongest predictor of home-court advantage. They
suggested that home teams should try to shoot more two-point shots and force
their opponent to take more two-point shot attempts. This help home teams have a
greater control of the game play and help maximize the benefits 
home-court advantage.

@@

Home-court advantage is the basic idea that the home team is more likely to win given 
they benefit from positive effects of a few factors we discussed earlier.
So laying a foundation of typical home-court advantage is crucial. Before
focusing on the 2017 to 2020 playoffs, we can take a quick look at home team win
percentages since 2010. Notice in Figure~\ref{fig:Fig1}, the 10 years before 2020, the home team
winning percentage ranged from around 0.56 to 0.7 and never dipped below 0.5. The
2020 bubble broke this historic pattern, dipping down below 0.5. Foreshadowing
the confirmation of the expectation that the effect of home-court advantage was removed
in the 2020 playoffs.

\jy{use `tbp' for figure/table locations instead of `H', unless it is
  required by the journal}

\jy{remake the figure~\ref{fig:Fig1}: make aspect 3:4 (height:width;
  increase the font size of the annonations; control the height/weight
  from within R now that we know how the figures will appear in the
  published version (so that you don't need to control width in latex.}

\jy{explain what the vertical lines are in all the figure captions}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=0.4\linewidth]{Fig1}
  \caption{Winning percentage of NBA home teams in the playoffs since
    2010, the green line denotes .500.}
  \label{fig:Fig1}
\end{figure}

Moving on to the main focus of the study, comparing 2020 to 2017-2019.
Figure~\ref{fig:Fig2} shows the histograms of the home (green) and
away scoring (red) for 2020 vs.~2017-2019. All histograms are
fairly bell shaped, which is important for statistical tests
designed for normally distributed data. There appears to be little
difference between the 2020 and 2017-2019 for home scoring. For
away scoring, a more pronounced shift to the right in 2020 is observed
compared to 2017-2019.

\jy{remake the figure~\ref{fig:Fig2}: make each panel aspect ratio 3:4; same for the
  next figures.}

@@

Our second target of inference is shooting percentage for home and away teams.
Figure~\ref{fig:Fig3} shows home shooting for two-pointers, three-pointers and
free throws for 2020 (top) vs.~2017--19 (bottom). The histograms appear to be fairly
similarly distributed between 2020 and 2017--19. Likewise, Figure~\ref{fig:Fig4},
shows the same percentages except for away teams. It appears that the
two-point shooting percentage for away teams has a small shift to the
right in 2020 relative to 2017-2019.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.4\linewidth]{Fig3}
  \caption{Histograms of home shooting percentages for two-
    pointers, three-pointers and free throws for 2020 (top) vs.~2017--19
    (bottom).}
  \label{fig:Fig3}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.4\linewidth]{Fig4}
  \caption{Histograms of away shooting percentages for two-pointers,
    three-pointers and free throws for 2020 (top) vs.~2017--19
    (bottom).}
  \label{fig:Fig4}  
\end{figure}

@@

Comparisons between 2020 and 2017--19 home and away teams were made on home team
winning percentage, total team scoring and two-point, three-point and free throw
shooting. Comparing the differences in these metrics for home and away teams in
2020 vs previous years will provide valuable insights to the understanding of
home-court advantage. We can see how going on the road may negatively impact
away performance and how playing at home may positively impact home performance.
If there are differences in scoring for home or away teams, the differences can
be used to show how home-court advantage affects the overall performance of home
and away teams. While testing for differences in shooting will provide added
context for how home-court advantage specifically affects performance.
Shooting percentages are not the only possible metrics affected by home-court
advantage, but they are the most obvious and likely most important one.

@@

\section{Results}

\jy{use booktabs package to add horizontal rules; replace 1 with
  1.0000; make sure ``Z-test'' is in the same font as in the text.}

\begin{table}[tbp]
  \caption{The results from the 9 tests(* denotes significant p-value at alpha=0.05)
  \\*Note: Home and Away scoring totals are divided by 100}
  \label{tab:table}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  & 2020 & 2017--19 & \multicolumn{2}{c}{P-value} & \multicolumn{2}{c}{Adjusted P-value}\\
\cmidrule(lr){4-5}\cmidrule(lr){6-7}
  &          &                & Z-test & Wilcoxon & Z-test & Wilcoxon\\
  \midrule
  Home Win & 0.482 & 0.613 & 0.0497* & 0.0400* & 0.4473 & 0.3598\\
Home Scoring & 1.101 & 1.081 & 0.2321 & 0.2985 & 1 & 1\\
Away Scoring & 1.091 & 1.040 & 0.0008* & 0.0004* & 0.0075* & 0.0035*\\
Home 2P & 0.523 & 0.515 & 0.4335 & 0.5719 & 1 & 1\\
Home 3P & 0.363 & 0.357 & 0.5733 & 0.8852 & 1 & 1\\
Home FT & 0.793 & 0.774 & 0.0692 & 0.0496* & 0.6228 & 0.4464\\
Away 2P & 0.536 & 0.504 & 0.0003* & 0.0003* & 0.0030 & 0.0023\\
Away 3P & 0.357 & 0.346 & 0.3256 & 0.3081 & 1 & 1\\
Away FT & 0.783 & 0.777 & 0.6601 & 0.8370 & 1 & 1\\
  \bottomrule
\end{tabular}
\end{table}

Starting from the top,
Table~\ref{tab:table} summarizes p-values of the nine hypotheses for both
\(z\)-tests and Wilcoxon tests. The p-values are all fairly similar for both
tests giving strong confidence in the conclusions drawn. Also, reported are
the point estimates of the two samples in each comparison.

\jy{add a reference to Bonferroni correction}

First, we see a statistically significant change
in home win percentage in 2020 from 2017--19, with a p-value of 0.0497 for the
\(z\)-test and 0.0400 for Fisher's exact test. The 95\% confidence
interval (CI) of \((-0.255, -0.008)\)
confirms our belief that home-court advantage was lost in the 2020 NBA 
playoffs. However, after accounting for
multiple tests using the Bonferroni correction, the p-values for both
tests are no longer significant. So, we may only cautiously say there is 
evidence that home-court advantage was
not a factor in 2020.

Home team performance did not seem to be negatively impacted by losing home-court
advantage like expected. Home scoring, two-point and three-point
shooting all show no significant difference, on average, between 2020 vs.
2017--19 based on p-values from both tests. However, the Wilcoxon test and \(z\)-test have conflicting results
for free throws. The \(z\)-test p-value of 0.0692 indicates no significant difference, while
the Wilcoxon test p-value of 0.0469 indicates a difference at the 5\% significance level. Since
the p-value of the Wilcoxon test is so close to significance level and neither p-value is significant
after a Bonferonni correction for multiple tests, this difference is likely not very meaningful.
There appears to be no strong evidence suggesting home teams played at
a lower level in 2020 than they did in previous years when they had home-court advantage.

@@

% \section*{acknowledgements}
% The authors thank the University of Connecticut and the UConn Department of Statistics.
%Note correct LaTeX quotations above. Do not use the " symbol, but rather double ` followed by double '

@@

\jy{are you interested in phd in statistics?}

% The Press Summary section is NOT optional.  Write a paragraph describing the paper in a manner suitable for the press; see previous journal editions for examples.
\section*{press summary}
The purpose of this study was to examine the 2020 NBA playoffs, which
were played inside of a bubble in Disney World because of the COVID-19
pandemic. The hope was to generate new insights about the effects of
home-court advantage because the bubble created an unprecedented
neutral playing field for the NBA. For the first time the effects of
home-court advantage on home and away teams could be easily separated
and studied individually, typically studies can only compare them
relative to each other. This study is focused on team scoring totals
and team shooting percentage on two-pointers, three-pointers, and free
throws. Comparing these measures for home teams and away teams in 2020
vs. 2017--2019 shows that the 2020 playoffs favored away teams more
than usual, particularly with two-point shooting and total
scoring. The implication of these findings is home-court advantage
seems to be the result of negative effects on away team, not positive
effects on home-team.
